Methods for Large Scale Learning to Rank

### 2014-10-24 report/Chapters/Background.tex
ERR fixed

where the product sequence part of the formula represents the chance that the user will stop at position $r$. $R_i$ in this formula represents the probability of the user being satisfied in his information need at position $i$ in the ranking.\\

The algorithm to compute \ac{ERR} is shown in Listing \ref{alg:err}. The algorithm requires relevance grades $g_i$, $1 \le i \le n$ and mapping function $R$ that maps relevance grades to probability of relevance.

\LinesNumbered
\begin{algorithm}[H]
 $p \leftarrow 1, ERR \leftarrow 0$\\
 \For{$r\leftarrow 1$ \KwTo $n$}{
	$R \leftarrow \mathcal{R}(rel_r)$\\
	$ERR \leftarrow ERR + p * \frac{R}{r}$\\
	$p \leftarrow p * (1-R)$
 }
 Output $ERR$
 \caption{The algorithm for computation of the \acs{ERR} metric, obtained from \cite{Chapelle2009}}
 \label{alg:err}
\end{algorithm}

>>>>

where the product sequence part of the formula represents the chance that the user will stop at position $r$. $R_i$ in this formula represents the probability of the user being satisfied in his information need after assessing the document at position $i$ in the ranking.\\

The algorithm to compute \ac{ERR} is shown in Listing \ref{alg:err}. The algorithm requires relevance grades $g_i$, $1 \le i \le n$ and mapping function $R$ that maps relevance grades to probability of relevance.\\

\LinesNumbered
\begin{algorithm}[H]
 $p \leftarrow 1, ERR \leftarrow 0$\\
 \For{$r\leftarrow 1$ \KwTo $n$}{
	$R \leftarrow \mathcal{R}(rel_r)$\\
	$ERR \leftarrow ERR + p * \frac{R}{r}$\\
	$p \leftarrow p * (1-R)$
 }
 Output $ERR$
 \caption{The algorithm for computation of the \acs{ERR} metric, obtained from Chapelle et al. \cite{Chapelle2009}}
 \label{alg:err}
\end{algorithm}
\vspace{0.5cm}
In this algorithm $\mathcal{R}$ is a mapping from relevance grades to the probability of the document satisfying the information need of the user. Chapelle et al. \cite{Chapelle2009} state that there are different ways to define this mapping, but they describe one possible mapping that is based on the Burges version \cite{Burges2005} of the gain function for \ac{DCG}:\\

$\mathcal{R}(r) = \frac{2^{r}-1}{2^{max\_rel}}$\\

\noindent where $max\_rel$ is the maximum relevance value present in the data set.
